Testing Data from the Toronto Paramedic Service

### 2023-02-03 scripts/01-data_import.qmd
Organized scripts into a folder

# Write data to a .csv file
write_csv(
  x = raw_response_data$`Land Ambulance Services`,
  file = "raw_response_data.csv"
)
```

@@

# Write data to a .csv file
write_csv(
  x = raw_emergent_care_data,
  file = "raw_emergent_care_data.csv"
)
```

@@

# Write data to a .csv file
write_csv(
  x = raw_incident_data$`2021`,
  file = "raw_incident_data.csv",
)
```

>>>>

# Write data to a .csv file
write_csv(
  x = raw_response_data$`Land Ambulance Services`,
  file = "../inputs/data/raw_response_data.csv"
)
```

@@

# Write data to a .csv file
write_csv(
  x = raw_emergent_care_data,
  file = "../inputs/data/raw_emergent_care_data.csv"
)
```

@@

# Write data to a .csv file
write_csv(
  x = raw_incident_data$`2021`,
  file = "../inputs/data/raw_incident_data.csv",
)
```

### 2023-02-03 scripts/02-data_testing.qmd
Organized scripts into a folder

<!--
#### Preamble ####
# Purpose: Testing Data from the Toronto Paramedic Service
# Prerequisites: Need to have downloaded the data using [inputs/data/data_import.qmd]
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses
-->
---
title: "Testing Data from the Toronto Paramedic Service"
format: html
author: "Sebastian Rodriguez"
---
```{r}
#### Workspace set-up ####
library(tidyverse)
library(janitor)
library(here)
library(readr)
```

@@

raw_incident_data

>>>>

---
title: "Testing Data from the Toronto Paramedic Service"
format: html
author: "Sebastian Rodriguez"
---
```{r}
#### Preamble ####
# Purpose: Testing Data from the Toronto Paramedic Service
# Prerequisites: Need to have downloaded the data using [inputs/data/data_import.qmd]
# Author: Sebastian Rodriguez
# Email: me@srod.ca
# Date: 3 February 2023
# GitHub: https://github.com/seb646/toronto-paramedic-responses
```

```{r}
#### Workspace set-up ####
library(tidyverse)
library(janitor)
library(here)
library(readr)
```

@@
